Gaze-dependent evidence accumulation predicts multi-alternative risky choice behaviour

### 2021-02-04 manuscript/main.tex
added seaborn and python-ternary references
updated numbers to figures

We find evidence for the attraction effect: The mean RST in attraction trials differed meaningfully from 0.5 (mean RST = 0.56, HDI$_{95}$ = [0.51, 0.60], mean $d$ = 0.49, HDI$_{95}$ = [0.10, 0.80]). 25 of 40 (62.5\%) participants had an RST above 0.5 in attraction trials. Notably, similar to previous work \parencite[e.g.,][]{trueblood2012MultialternativeContextEffects} a subgroup of participants (9 of 40, 22.5\%) showed particularly strong attraction effects with individual RSTs above 0.7. We could not, however, find evidence that these individuals used the dominance relationship as a simplifying choice rule (see \nameref{sec:supplement}). To allow comparisons with other studies that quantified context effects as the difference between choice shares between targets and competitors, we also report these differences: In attraction trials, the average difference was 0.12 (HDI$_{95}$ = [0.01, 0.20], mean $d$ = 0.48, HDI$_{95}$ = [0.11, 0.85], Figure \ref{fig:cfx}b).

@@

Next, we tested whether participants' eye movements were affected by the set of available alternatives, similar to their choices. We therefore computed each alternative's relative dwell time in a trial by summing the duration of all fixations durations towards it, and normalizing to the sum of all fixations in the trial. Both patterns of context effects of choice behaviour were present in the relative dwell data: Target options received greater relative dwell time than competitors in attraction (mean difference = 0.014, HDI$_{95}$ = [0.004, 0.024], mean $d$ = 0.53, HDI$_{95}$  = [0.15, 0.93], Figure \ref{fig:cfx}c) and compromise trials (mean difference = 0.022, HDI$_{95}$  = [0.014, 0.030], mean $d$ = 0.90, HDI$_{95}$  = [0.53, 1.31], Figure \ref{fig:cfx}f). Targets and competitors also received greater relative dwell time than decoys in both trial types.

@@

\subsection*{Software}
The task was programmed in MATLAB (The Mathworks Inc., USA) using the PsychToolBox \parencite{brainard1997psychophysics}. Data processing and analyses were done in Python with numpy \parencite{harris2020array}, scipy \parencite{jones2001SciPyOpenSource} and pandas \parencite{mckinney2012PythonDataAnalysis} libraries. Bayesian analyses were implemented in PyMC3 \parencite{salvatier2016ProbabilisticProgrammingPython}, mixed models used bambi \parencite{yarkoni2016BambiSimpleInterface}. Exceedance probabilities were computed in MATLAB using SPM12 \parencite{penny2011statistical}. Figures were created using matplotlib \parencite{hunter2007Matplotlib2DGraphics}.

>>>>

We find evidence for the attraction effect: The mean RST in attraction trials differed meaningfully from 0.5 (mean RST = 0.56, HDI$_{95}$ = [0.51, 0.60], mean $d$ = 0.49, HDI$_{95}$ = [0.10, 0.80]). 25 of 40 (62.5\%) participants had an RST above 0.5 in attraction trials. Notably, similar to previous work \parencite[e.g.,][]{trueblood2012MultialternativeContextEffects} a subgroup of participants (9 of 40, 22.5\%) showed particularly strong attraction effects with individual RSTs above 0.7. We could not, however, find evidence that these individuals used the dominance relationship as a simplifying choice rule (see \nameref{sec:supplement}). To allow comparisons with other studies that quantified context effects as the difference between choice shares between targets and competitors, we also report these differences: In attraction trials, the average difference was 0.12 (HDI$_{95}$ = [0.01, 0.20], mean $d$ = 0.48, HDI$_{95}$ = [0.10, 0.85], Figure \ref{fig:cfx}b).

@@

Next, we tested whether participants' eye movements were affected by the set of available alternatives, similar to their choices. We therefore computed each alternative's relative dwell time in a trial by summing the duration of all fixations durations towards it, and normalizing to the sum of all fixations in the trial. Both patterns of context effects of choice behaviour were present in the relative dwell data: Target options received greater relative dwell time than competitors in attraction (mean difference = 0.014, HDI$_{95}$ = [0.004, 0.024], mean $d$ = 0.53, HDI$_{95}$  = [0.15, 0.93], Figure \ref{fig:cfx}c) and compromise trials (mean difference = 0.022, HDI$_{95}$  = [0.014, 0.030], mean $d$ = 0.90, HDI$_{95}$  = [0.53, 1.30], Figure \ref{fig:cfx}f). Targets and competitors also received greater relative dwell time than decoys in both trial types.

@@

\subsection*{Software}
The task was programmed in MATLAB (The Mathworks Inc., USA) using the PsychToolBox \parencite{brainard1997psychophysics}. Data processing and analyses were done in Python with numpy \parencite{harris2020array}, scipy \parencite{jones2001SciPyOpenSource} and pandas \parencite{mckinney2012PythonDataAnalysis} libraries. Bayesian analyses were implemented in PyMC3 \parencite{salvatier2016ProbabilisticProgrammingPython}, mixed models used bambi \parencite{yarkoni2016BambiSimpleInterface}. Exceedance probabilities were computed in MATLAB using SPM12 \parencite{penny2011statistical}. Figures were created using matplotlib \parencite{hunter2007Matplotlib2DGraphics}, seaborn \parencite{waskom2020seaborn} and python-ternary \parencite{pythonternary}.
